markov_chains

### 2017-03-18 San Antonio/markov_chains.Rmd
completed transition matrix

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(plyr)
require(RcppRoll)
require(markovchain)
require(reshape)
knitr::opts_knit$set(root.dir = "~/Documents/Violation_Project")
setwd("~/Documents/Violation_Project")

@@

```{r}
clustering
freq_table

clustering$centers
```

@@

Markov Chain stuff
```{r}
markov <- function(x){
  x <- as.integer(x)
  cluster_seq_raw <- x[!is.na(x)]
  if(length(cluster_seq_raw) > 1){
    cluster_sequence <- cluster_seq_raw[2:length(cluster_seq_raw)]
    cur_markov_chain <- markovchainFit(data=cluster_sequence)
    return (list("mine_id" = x[1], "markov_chain" = cur_markov_chain$estimate, "num_rows" = length(cluster_seq_raw)))
  }
  return (list("mine_id" = x[1], "markov_chain" = NA, "num_rows" = 0))
}
```

@@

```{r}
num_rows_ind <- sapply(result, "[[", 3)
weights <- num_rows_ind/sum(num_rows_ind)
markov_chains_ind <- sapply(result, "[[", 2)
aggregated_markov_chain <- weighted.mean(markov_chains_ind, weights)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(plyr)
require(RcppRoll)
require(markovchain)
require(reshape)
```
```{r setting directories}
knitr::opts_knit$set(root.dir = "~/Documents/Violation_Project")
setwd("~/Documents/Violation_Project")

@@

```{r}
clustering
freq_table
```

@@

Markov Chain function
```{r}
markov <- function(x){
  x <- as.integer(x)
  cluster_seq_raw <- x[!is.na(x)]
  if(length(cluster_seq_raw) > 1){
    cluster_sequence <- cluster_seq_raw[2:length(cluster_seq_raw)]
    cur_markov_chain <- markovchainFit(data=cluster_sequence)
    return (list("mine_id" = x[1], "markov_chain" = cur_markov_chain$estimate@transitionMatrix, "num_rows" = length(cluster_seq_raw)))
  }
  return (list("mine_id" = x[1], "markov_chain" = NA, "num_rows" = 0))
}
```

@@

```{r}
num_rows_ind <- sapply(result, "[[", 3)
weights <- num_rows_ind/sum(num_rows_ind)

markov_chains_ind <- sapply(result, "[[", 2)

weighted_transition <- mapply(function(x,y) x * y, x = weights, y = markov_chains_ind)

#adding matrix of different dimentions, source: http://stackoverflow.com/questions/13571359/join-and-sum-not-compatible-matrices
add_matrices_1 <- function(...) {
  a <- list(...)
  cols <- sort(unique(unlist(lapply(a, colnames))))
  rows <- sort(unique(unlist(lapply(a, rownames))))
  out <- array(0, dim=c(length(rows), length(cols)), dimnames=list(rows,cols))
  for(M in a) { out[rownames(M), colnames(M)] <- out[rownames(M), colnames(M)] + M }
  return(out)
}

final_transition<- matrix(rep(0,times= 9), ncol = 3, nrow = 3)
colnames(final_transition) <- c(1,2,3)
rownames(final_transition) <- c(1,2,3)

for(i in 1:length(weighted_transition)){
  final_transition <- add_matrices_1(final_transition,weighted_transition[[i]])
}
final_transition
